Psychological Needs During Intergroup Contact

### 2022-01-16 manuscript.tex
limitations added

\subsection{Limitations}
to be discussed, potentially:
\begin{enumerate}
    \item migrants are not refugees (generalizability potentially even more relevant?)
    \item minority perspective only
    \item lagged effects left for future studies (potentially not relevant, time scale)
    \item ESM: real-life data comes at the expense of having short/single item operationalizations
    \item are we presenting a relativistic model? i.e. are we breaking theoretical ground? at the end we are saying: it always depends what the main goal of the individual is. Is this hyper applied but not really theoretical? (just a though :) ) Make sure to discuss: (1) practical relevance and (2) core situational need as initial test of the role of motivations.
\end{enumerate}

\subsection{Implications}
to be discussed, potentially:
\begin{enumerate}
    \item feasible to collect large amount of data on intergroup contact using ESM method (do we have a formR ref in there?; set up is feasible but not the easiest; maybe even advertise the reusability of the formR survey?)
    \item role of motivation in intergroup contact promising (potential for interventions, e.g., most immediate to the data: settlement practices). 
    \item potential to identify context specific needs
\end{enumerate}

>>>>

\subsection{Limitations}
% (1) Sample = minority and (voluntary) migrants, (2) Methodology = short scales (reliability) and no lagged effects, (3) Core Need Concept = non-specific
As with any approach our studies are not without practical and theoretical limitations. One limitation is our choice of samples. While we believe that a need–based mechanism should be relevant to any inter-group contact, our sample has focused on a minority- and (voluntary) migrant perspective. Without additional evidence it thus remains difficult to judge whether motivational effects will generalize to other migrant groups (e.g., forced migrants), other intergroup contexts (e.g., gender- or sexual orientation groups), and to majority groups in their outgroup attitudes. We know of no research that for other contexts psychological needs would not be relevant (once existential needs are met) but future research may extend our findings to other contexts to build an even broader understanding of psychological needs in intergroup contacts. A second limitation lies in our methodology. While extensive longitudinal data is close to the real-life events this method comes at the expense of longer and more robust scales. Long and repetitive scales are often not feasible in extensive longitudinal methods because of the increased burden to the participants. To circumvent this shortcoming, we have ensured that the measures we used were, whenever possible, based on past validations. However, the circumstance remains that extensive longitudinal data often does not allow the same scrutiny of measurement reliability as single–shot cross–section data sets. An additional methodological question lies in the unexplored potential of the longitudinal aspects of our data. For our research questions we have focused on contemporaneous effects within the data set, yet future investigations should seek to extend the mechanism to developmental trajectories within and between participants. And finally, our conceptualization of core situational needs has been focused on the most essential test of a motivational mechanism. This has come at the expense of specificity in the situational needs (i.e., we have not explored which exact needs people had during their interactions). With the adaptive measurement we have proposed such an investigation would be possible (e.g., by clustering or classifying the free text entries) but would not have been relevant to our theory–focused research question. Nonetheless, future research may explore which exact needs are most important in different intergroup contexts.

\subsection{Implications}
From our results we can draw a number of

to be discussed, potentially:
\begin{enumerate}
    \item feasible to collect large amount of data on intergroup contact using ESM method (do we have a formR ref in there?; set up is feasible but not the easiest; maybe even advertise the reusability of the formR survey?)
    \item role of motivation in intergroup contact promising (potential for interventions, e.g., most immediate to the data: settlement practices). 
    \item potential to identify context specific needs
\end{enumerate}
